Continuous Generalization of Buildings \protect\\ by Growing and Merging

### 2017-08-17 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
added texts of sections Methodology and Case study

\newcommand{\e}[1]{\times 10^{#1}}
\newcommand{\fig}{Fig.~}
\newcommand{\eq}{Eq.~}

@@

\subsection{Grouping buildings based on buffering}
We group buildings based on the buffers of the buildings. 
We buffer each building with distance $d_G + \frac{d_\epsilon}{2}$, 
where distance $d_G$ is the growing amount of each building. 
Parameter $d_\epsilon$ is the least distance allowed between two buildings.
We grow an additional $\frac{d_\epsilon}{2}$ so that if two buffers overlap, 
the corresponding two buildings will become too close during our growing step.
The two buildings are in the same group.

@@

\subsection{Enlarging and merging buildings}

>>>>

\newcommand{\e}[1]{\times 10^{#1}}
\newcommand{\fig}{Fig.~}
\newcommand{\eq}{Eq.~}
\newcommand{\sect}{Sec.~}

@@

\subsection{Grouping buildings based on buffering}
\label{sec:Grouping}
We group buildings based on the buffers of the buildings. 
We buffer each building with distance $d_G + \frac{d_\epsilon}{2}$, 
where distance $d_G$ is the growing amount of each building. 
Parameter $d_\epsilon$ is the least distance allowed between two buildings.
We grow an additional $\frac{d_\epsilon}{2}$ so that if two buffers overlap, 
the corresponding two buildings will become too close during our growing step.
The two buildings are in the same group.

@@

\subsection{Enlarging and merging buildings for goal map}
For each pair of buildings in the same group, 
we find the smallest distance between them.
We connect the buildings by adding an edge from the nearest points.
We find a minimum spanning tree of the buildings using Prim's algorithm 
\parencite{Prim1957}.
We enlarge and merge buildings as the way we do in \sect\ref{sec:Grouping}.
